### 2017-05-22 paper/documents/0.abstract.tex
- update paper

This is abstract\cite{eggert2015classification}

>>>>

Multi-player online battle arena games are the most successful games. Every players have own specific roles in this team based game. Dota2 is the most popular for this games. This paper analyzing player roles and their behavior using supervised machine learning and also investigates the applicability of feature normalization to enhance accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files. Using attribute evaluation techniques, we are able to reduce a larger set of candidate attributes down to a manageable number. Random Forest is the most stable and best performing classifier in our results.
